BETTING AND BELIEF: PREDICTION MARKETS AND ATTRIBUTION OF CLIMATE CHANGE

### 2016-06-28 arxiv.Rnw
Switched from ggplot2 to jgplot2 (my fork of Hadley's ggplot2 which implements outlier.alpha argument to geom_boxplot). If necessary, install from devtools::install_github('jonathan-g/jgplot2', ref='jgplot2') Updated citations to WAIC.

Warming coefficients for each model were determined by linear regression of historical temperatures from 1880--2014 against the historical values for each model's forcing term. The noise model was determined by fitting an $\ARMA(p,q)$ model to the residuals from the regression, using the \href{http://mc-stan.org}{Stan} probabilistic modeling language and the \href{https://cran.r-project.org/web/packages/rstan/}{\texttt{rstan}} package \shortcite{Stan2016,RStan2016}. Stan proved more numerically stable than the \Rstat\ \href{http://CRAN.R-project.org/package=nlme}{\texttt{nlme}} package \shortcite{nlme_2016} for fitting ARMA noise models. We identified the optimal model for the auto-correlated noise term by performing the regression analysis for all combinations of $p, q \in [0,1,2]$ and using the Watanabe-Akaike Information Criterion to select the optimal noise model \shortcite{Vehtari_2015}. In both cases (TSI and $\log\ce{CO2}$), the optimal noise model was $\AR(1)$.

>>>>

Warming coefficients for each model were determined by linear regression of historical temperatures from 1880--2014 against the historical values for each model's forcing term. The noise model was determined by fitting an $\ARMA(p,q)$ model to the residuals from the regression, using the \href{http://mc-stan.org}{Stan} probabilistic modeling language and the \href{https://cran.r-project.org/web/packages/rstan/}{\texttt{rstan}} package
\shortcite{Stan2016,RStan2016}.
Stan proved more numerically stable than the \Rstat\ \href{http://CRAN.R-project.org/package=nlme}{\texttt{nlme}} package
\shortcite{nlme_2016}
for fitting ARMA noise models. We identified the optimal model for the auto-correlated noise term by performing the regression analysis for all combinations of $p, q \in [0,1,2]$ and using the Widely Applicable Information Criterion to select the optimal noise model \shortcite{Watanabe_2013,Gelman_2014}. In both cases (TSI and $\log\ce{CO2}$), the optimal noise model was $\AR(1)$.

### 2016-06-28 prediction_market_wsc.Rnw
Switched from ggplot2 to jgplot2 (my fork of Hadley's ggplot2 which implements outlier.alpha argument to geom_boxplot). If necessary, install from devtools::install_github('jonathan-g/jgplot2', ref='jgplot2') Updated citations to WAIC.

Warming coefficients for each model were determined by linear regression of historical temperatures from 1880--2014 against the historical values for each model's forcing term. The noise model was determined by fitting an $\ARMA(p,q)$ model to the residuals from the regression, using the \href{http://mc-stan.org}{Stan} probabilistic modeling language and the \href{https://cran.r-project.org/web/packages/rstan/}{\texttt{rstan}} package \shortcite{Stan2016,RStan2016}. Stan proved more numerically stable than the \Rstat\ \href{http://CRAN.R-project.org/package=nlme}{\texttt{nlme}} package \shortcite{nlme_2016} for fitting ARMA noise models. We identified the optimal model for the auto-correlated noise term by performing the regression analysis for all combinations of $p, q \in [0,1,2]$ and using the Watanabe-Akaike Information Criterion to select the optimal noise model \shortcite{Vehtari_2015}. In both cases (TSI and $\log\ce{CO2}$), the optimal noise model was $\AR(1)$.

@@

We thank Yevgeniy Vorobeychik for feedback on this project and Manuel Naumovich Velasco for sharing the data from his Total Solar Irradiance prediction.
U.S. National Science Foundation grants EAR-1416964, EAR-1204685, and 1526860 partially supported this research. The funder had no role in study design, data collection and analysis, decision to publish, or preparation of the manuscript. All views expressed are the authors' and not the funder's.
%We also thank the authors of \href{http://www.r-project.org}{\textsf{R}} \shortcite{r_core}
%and
%\href{http://mc-stan.org}{Stan} \shortcite{Stan2016}.
%This manuscript was prepared using
%RStudio \shortcite{rstudio} and
%knitr \shortcite{xie_knitr_2014}.

>>>>

Warming coefficients for each model were determined by linear regression of historical temperatures from 1880--2014 against the historical values for each model's forcing term. The noise model was determined by fitting an $\ARMA(p,q)$ model to the residuals from the regression, using the \href{http://mc-stan.org}{Stan} probabilistic modeling language and the \href{https://cran.r-project.org/web/packages/rstan/}{\texttt{rstan}} package \shortcite{Stan2016}. Stan proved more numerically stable than the \Rstat\ \href{http://CRAN.R-project.org/package=nlme}{\texttt{nlme}} package
%\shortcite{nlme_2016}
for fitting ARMA noise models. We identified the optimal model for the auto-correlated noise term by performing the regression analysis for all combinations of $p, q \in \lbrace 0,1,2 \rbrace$ and using the Widely Applicable Information Criterion to select the optimal noise model \shortcite{Watanabe_2013,Gelman_2014}. In both cases (TSI and $\log\ce{CO2}$), the optimal noise model was $\AR(1)$.

@@

We thank Yevgeniy Vorobeychik for feedback on this project and Manuel Naumovich Velasco for sharing the data from his Total Solar Irradiance prediction.
U.S. National Science Foundation grants EAR-1416964, EAR-1204685, and 1526860 partially supported this research.
% The funder had no role in study design, data collection and analysis, decision to publish, or preparation of the manuscript.
All views expressed are the authors' and not the funder's.
%We also thank the authors of \href{http://www.r-project.org}{\textsf{R}} \shortcite{r_core}
%and
%\href{http://mc-stan.org}{Stan} \shortcite{Stan2016}.
%This manuscript was prepared using
%RStudio \shortcite{rstudio} and
%knitr \shortcite{xie_knitr_2014}.
